---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# argos

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/argos)](https://CRAN.R-project.org/package=argos)
<!-- badges: end -->

The goal of argos is to sinplify and standardize interacting with databases
that use the OMOP Common Data Model or PCORnet Common Data Model.  It collects
affordances and recommended practices developed by PEDSnet in its conduct of
clinical research.

## Installation

You can install the development version of argos like so:

``` r
devtools::install_github('PEDSnet/argos')
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(argos)

argos::new_request('/path/to/request')
```

## End
